Desert Ant Behaviour: Simulating Movement and Navigation

### 2011-12-16 documentation/report.tex
cites

\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{subfig}
\usepackage{amssymb, amsmath}
\usepackage{hyperref}
\usepackage{pdfpages}
\usepackage[framed,numbered,autolinebreaks,useliterate]{mcode/mcode}

@@

Because of the nature of the problem we chose to design our simulation around a time-discrete step-based model of an ant. We chose to simulate only one ant at a time, because we don’t think that an higher number of ants would make much of a difference considering the vast space in the deserts. Therefore we can leave out influences of near ants like separation and cohesion (compare Agent Based Modeling\cite{soms}).

@@

\subsubsection{Move}
The move method is the heart of the ant class: it accepts any general direction vector as input and sets the new position of the ant as a result. A general direction input can be calculated in the method “find food” or “return to nest”. It also handles all the checking for obstacles. Move is invoked in every time-step. Because the ant has only a choice of 8 possible next positions the method has to calculate a new direction vector to one of the first order Moore neighbours (figure \ref{moore}).
\begin{figure}
\centering
\includegraphics[width=6cm]{images/Mooreneighbours.pdf}
\caption[First order moore neighbours]{First order Moore neighbours}
\label{moore}
\end{figure}

@@

\listoffigures

>>>>

\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{subfig}
\usepackage{amssymb, amsmath}
\usepackage{hyperref}
\usepackage{pdfpages}
\usepackage[framed,numbered,autolinebreaks,useliterate]{mcode/mcode}
\usepackage{url}

@@

Because of the nature of the problem we chose to design our simulation around a time-discrete step-based model of an ant. We chose to simulate only one ant at a time, because we don’t think that an higher number of ants would make much of a difference considering the vast space in the deserts. Therefore we can leave out influences of near ants like separation and cohesion (compare Agent Based Modeling)\cite{soms}.

@@

\subsubsection{Move}
The move method is the heart of the ant class: it accepts any general direction vector as input and sets the new position of the ant as a result. A general direction input can be calculated in the method “find food” or “return to nest”. It also handles all the checking for obstacles. Move is invoked in every time-step. Because the ant has only a choice of 8 possible next positions the method has to calculate a new direction vector to one of the first order Moore neighbours (figure \ref{moore}).
\begin{figure}
\centering
\includegraphics[width=6cm]{images/Mooreneighbours.pdf}
\caption[First order moore neighbours]{First order Moore neighbours\cite{soms,pic1}}
\label{moore}
\end{figure}

@@

\newpage
\listoffigures
